draft_final_assignment

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

## Creating party variable
```{r }
df$party <- ifelse(df$cosponsor_D_perc > 0.66, "Democrat", ifelse(df$cosponsor_R_perc > 0.66, "Republican", "Both"))
```

>>>>

## Creating party variable
```{r }
#if two thirds of the sponsors are democrats, we consider the bill democrat-dominated
#same for republicans
#if there is no clear majority, they are "Both"
df$party <- ifelse(df$cosponsor_D_perc > 0.66, "Democrat", ifelse(df$cosponsor_R_perc > 0.66, "Republican", "Both"))
```
